Binning Strategies and Related Loss for Large Data

### 2015-04-06 Paper.Rnw
ylim

<<SpatialLossCompare,echo=F,include=T,eval=T,fig.width=8, fig.height=3, out.width='.8\\linewidth', fig.pos='h',fig.align='center',tidy=F, cache=TRUE, fig.show='hold',fig.cap="Lineplots for net spatial loss over a range of bin sizes for standard and random binning of the fine version of the simulated data from each bivariate distribution.">>= 
spatlossdat <- read.csv("SpatialLossData.csv",header=TRUE)
# use all the square bins to plot bin width against proportion of max spataial loss
spatlossdatSquareBins <- spatlossdat[spatlossdat$widthx==spatlossdat$widthy,]
qplot(widthx,totalSpatialLoss,geom="path",colour=bintype, linetype=bintype,
      data=spatlossdatSquareBins,group=bintype, facets=.~distrib, size=I(1)) +
  theme_bw() + ylab("Net Spatial Loss") +
  xlab("Width/Height of Square Bins")
@

>>>>

<<SpatialLossCompare,echo=F,include=T,eval=T,fig.width=8, fig.height=3, out.width='.8\\linewidth', fig.pos='h',fig.align='center',tidy=F, cache=TRUE, fig.show='hold',fig.cap="Lineplots for net spatial loss over a range of bin sizes for standard and random binning of the fine version of the simulated data from each bivariate distribution.">>= 
spatlossdat <- read.csv("SpatialLossData.csv",header=TRUE)
# use all the square bins to plot bin width against proportion of max spataial loss
spatlossdatSquareBins <- spatlossdat[spatlossdat$widthx==spatlossdat$widthy,]
qplot(widthx,totalSpatialLoss,geom="path",colour=bintype, linetype=bintype,
      data=spatlossdatSquareBins,group=bintype, facets=.~distrib, size=I(1)) +
  theme_bw() + ylab("Net Spatial Loss") +
  xlab("Width/Height of Square Bins") + ylim(c(0, 1100000))
@
